Multisensor Architecture for an Intersection Management System

### 2015-03-20 ch2-mdf_ims.tex
Some corrections and modifications

Different types of applications and systems appear in order to address this issues. Some tasks these systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others. Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).

@@

Other application are traffic-control oriented, rather than to sensing and data-processing stage. The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety. Many works have been done and although its objective is the same, are diversity between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).

>>>>

Different types of applications and systems are conceived to address these issues. Some tasks those systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others. Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).

@@

Other application are traffic-control oriented, rather than to sensing and data-processing stage. The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety. Many works have been done and although their objective is the same, are diverse between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).
